%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Military Service}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Cyber R\&D Team Lead} % Degree
    {Unit 8200} % Institution
    {Tel Aviv, Israel} % Location
    {May 2022 ‑ May 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Formed a new team of Cyber R\&D developers to solve crucial problems in the core of the unit’s operations.}
        \item {Multidisciplinary team operating at cyber security and intelligence interface. Worked in \textbf{Python, C, ASM, HTML/JS, and SQL}.}
        \item {Mentored new team members and developed the team's training program from the ground up.}
        \item{Led numerous cross-team projects, managing timelines, coordinating tasks, and ensuring successful delivery}
      \end{cvitems}
    }
  
  \cventry
    {Recruitment officer for ARAM, GA‘ASH, and ARAZIM} % Degree
    {Unit 8200} % Institution
    {Tel Aviv, Israel} % Location
    {Aug 2021 ‑ May 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Conducted over 500 interviews with all relevant applicants. }
        \item {Oversaw and modified the entire recruitment process for the most elite tracks of Unit 8200. }
        \item {Recipient of the "Nadav" scholarship for exceptional research, as the sole master's student selected.}
        \item {Started During the third year of the BSc, and was a full-time officer at the IDF for most of the degree}
      \end{cvitems}
    }
    
  \cventry
    {R\&D engineer} % Degree
    {Unit 8200} % Institution
    {Tel Aviv, Israel} % Location
    {Feb 2019 ‑ Aug 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      \item{Expertise in practical cyber security operations in Windows OS‑based environments. Worked mainly in \textbf{Python and C++}.}
      \item{Expertise in complex networks and cyber-security within large organizations.}
      \item{Developed new systems and optimized existing methods to increase efficiency and achieve outcomes previously unattainable.}
      \end{cvitems}
    }
    
  % \cventry
  %   {Bar-Ilan Math Program} % Degree
  %   {Bar-Ilan University} % Institution
  %   {Tel Aviv, Israel} % Location
  %   {Sep 2012 - Jun 2015} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) bullet points
  %       \item {Started the program a year early, finished the Math $5$-units with honors at the ninth grade.}
  %     \end{cvitems}
    % }
%---------------------------------------------------------
\end{cventries}
