%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {PhD in Computer Science} % Degree
    {Bar-Ilan University} % Institution
    {Ramat Gan, Israel} % Location
    {Oct 2023 - Now} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Won the prestige Clore scholarship for exceptional Phd Students.}
        \item {Won the The Feder Family Award for Best Student Work in Communications.}
        \item {Studying distance-related graph problems. \textbf{Distance Oracles.}} 
        \item {Submitted multiple papers to prestige conferences and journal.}
        \item {Started During my service at the IDF. Currently studying full-time.}
      \end{cvitems}
    }
  
  \cventry
    {MSc in Computer Science} % Degree
    {Bar-Ilan University} % Institution
    {Ramat Gan, Israel} % Location
    {Oct 2017 - Mar 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Researched \textbf{girth approximations}, published and presented two papers in the prestigious conferences of \textbf{SODA'22} and \textbf{SODA'23}. }
        \item {Collaborated with \textbf{leading global experts} in distance-related problems. }
        \item {Recipient of the "Nadav" scholarship for exceptional research, as the sole master's student selected.}
        \item {Started During the third year of the BSc, and was a full-time officer at the IDF for most of the degree.}
      \end{cvitems}
    }
    
  \cventry
    {BSc in Computer Science and Pure Mathematics} % Degree
    {Bar-Ilan University} % Institution
    {Ramat Gan, Israel} % Location
    {Jul 2015 - Aug 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      \item{Graduated with honors at the age of $17$.}
      \item{Started in 9th grade and pursued studies in parallel with my high school education.}
      \end{cvitems}
    }
    
  % \cventry
  %   {Bar-Ilan Math Program} % Degree
  %   {Bar-Ilan University} % Institution
  %   {Tel Aviv, Israel} % Location
  %   {Sep 2012 - Jun 2015} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) bullet points
  %       \item {Started the program a year early, finished the Math $5$-units with honors at the ninth grade.}
  %     \end{cvitems}
    % }
%---------------------------------------------------------
\end{cventries}
