\documentclass{article}

\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{arrows,automata,patterns}
\usepackage{enumerate}
\usepackage{makecell}

\usepackage{silence}
\WarningFilter[pdftoc]{hyperref}{Token not allowed in a PDF string}

\usepackage{hyperref}


%\usepackage{graphicx} % Required for inserting images
\usepackage[linesnumbered,ruled,vlined,boxed,algo2e]{algorithm2e}
\usepackage{nicefrac}
\usepackage{amsmath}
\usepackage{float}
\usepackage{mathtools}
\usepackage{amsthm}
\usepackage{multirow}
\usepackage{fullpage}
\usepackage{amsfonts}
\newtheorem{lemma}{Lemma}
\newtheorem{claim}{Claim}[lemma]


\newtheorem{theorem}{Theorem}
\newtheorem{property}[lemma]{Property}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{remark}[lemma]{Remark}
\newtheorem{problem}{Problem}

\newenvironment{reminder}[1]{\smallskip
\noindent {\bf #1. }\em}{}
\usepackage{xcolor}

\usepackage{silence}
\WarningFilter[pdftoc]{hyperref}{Token not allowed in a PDF string}

\begin{document}
Dear Members of the Scholarship Committee,

I am honored to be considered for this distinguished scholarship and deeply appreciate the opportunity to present my candidacy. My academic journey, professional experiences, and personal achievements reflect a commitment to excellence and a passion for bridging research with impactful applications.

My academic path began early. As a high school student, I was a member of Israel’s Mathematics and Computer Science teams, ranking among the top 15 students nationwide. This sparked my passion for problem-solving and set the foundation for my research career. At 16, I began my undergraduate studies, pursuing a dual focus in mathematics and computer science.

I went on to pursue a Master’s in algorithms, focusing on open problems in graph theory. My thesis on girth—the shortest cycle in graphs—led to novel algorithms with improved trade-offs, earning me the "Nadav" scholarship for research excellence. I later extended this work to weighted graphs, achieving groundbreaking results using advanced techniques, including Spira’s algorithm and computational geometry.

As a PhD candidate, I am studying Distance Oracles—data structures for efficient distance estimation in graphs. My contributions include improving the construction time for Wulff-Nilsen’s oracle [SODA`12] and developing novel oracles with better query times. This paper is currently under review for the prestigious STOC conference.

Beyond academia, I pursued intellectual challenges in chess, ranking among the top five players in Israel during middle school and recently achieving 3rd place in the Bughouse World Championship with my brother. These experiences taught me focus, adaptability, and teamwork, which inform my academic and professional work.

At 18, I began teaching as a Teaching Assistant for algorithms and other foundational courses, honing my communication skills and passion for mentoring. I also served five years in the IDF’s elite 8200 Unit, specializing in cyber intelligence. As a team leader and recruitment officer, I oversaw projects and conducted over 500 interviews, sharpening my decision-making, leadership, and problem-solving skills.

I have actively contributed to the community, participating in Model UN to improve my public speaking and negotiation skills, and tutoring immigrant students in math, Hebrew, and science. These experiences reinforced my belief in the power of education and inclusion.

As an algorithm engineer, I have deepened my understanding of translating theoretical advancements into scalable, real-world solutions, and my work has earned multiple accolades, including the "Nadav" scholarship and several awards during my Bachelor’s degree.

This scholarship would provide essential support for my continued research, allowing me to delve deeper into foundational problems in algorithms and develop innovative solutions that address both theoretical and practical challenges.

Thank you for considering my application. I am deeply grateful for this opportunity and look forward to contributing further to the field of algorithms with your support.

Sincerely,
Avi Kadria
\end{document}
